\section{Conclusion}
The impact of social networks on society, politics, and personal well-being is not likely to decrease in the future. This relationship between social networks and its users is an asymmetrical one, however: Users cannot gain insight into how these social networks work, how the algorithms select contents, and most importantly how social networks might skew one's perception of reality. Already today, this poses a real threat to society as the engagement-driven recommender algorithms support a rise of populism (\cite{groshekHelpingPopulismWin2017}).

This study examined ways to automatically collect, process, and store large amounts of Twitter data. Then, using visualizations, this data set was made accessible to laymen. Using such a tool to examine how specific topics are discussed on Twitter makes it easier for users to put discussions into perspective. Tools like the one presented in this study can even be seen as the future of journalism: not a one-way street of pre-analyzed data, but rather giving readers \say{the tools to hold institutions in your life accountable for their choices}---institutions like Facebook or Twitter (\cite{angwinMakingPrivacyPersonal2020}).

The visualizations were tested in user studies to see if laymen can indeed gain meaningful insights from the visualizations. While some potential for improvement was found, the results generally hint at laymen indeed being capable of reading visualizations, as long as some rules and guidelines are followed.

The results of this study  show that Big Data analysis can be democratized and made publicly available. Instead of having to wait for 'professional' analyses, like the Netflix documentary \emph{The Social Dilemma}\footnote{https://www.imdb.com/title/tt11464826/, last visited on 15.10.2020}, users could use tools to analyze that present data in a way that laymen can read and understand. This could give them the means to check their own opinions and world-views against others, leading to more civilized and understanding discussions.

%- the impact of social media on society, politics, and well-being is not likely to decrease in future years. Meanwhile, users of social media cannot get an objective view of the network, as they mostly see contents that are chosen by an engagement-driving algorithm. This could pose a real threat to society and a rise of populism (Groshek2017).

%- this study examined ways to automatically collect, process, and store large amounts of Twitter data and make such a dataset accessible to laymen. This could give them the tools to examine how specific topics are discussed on social media, making this less opaque.

%- The visualizations were tested in user studies to see if laymen can gain meaningful insights from the visualizations.

%- the user study showed that laymen could gain insight from these visualizations while analyzing further improvements that future studies could focus on.